\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-12 MasterDefense/main.tex
New

\begin{document}
\setbeamertemplate{itemize item}{\normalsize\textbullet}
\begin{frame} % ← 不使用 [plain]，保留 Madrid 顶部蓝条
  \titlepage
\end{frame}
\section{Motivation}
\begin{frame}{Why We Study Scattering Amplitudes?}
  \begin{enumerate}
    \item \textbf{Bridge between theory and experiment}
    \begin{itemize}
      \item Core prediction targets for high-energy collider experiments such as the LHC
      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
    \end{itemize}
    \pause
    \item \textbf{Reveal deep structures of quantum field theory}
    \begin{itemize}
      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or AdS/CFT correspondence
    \end{itemize}
  \end{enumerate}
\end{frame}

@@

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
$n$ pt. amplitudes & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
\# of diag.      & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
\hline
\end{tabular}
\end{center}
\pause
\centering
\textcolor{red}{The number of Feyman diagrams grow quite rapidly!}

@@

\begin{frame}
\frametitle{Conventional Computation}
\hypertarget{conv}{}
    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
\begin{figure}
  \centering
  \includegraphics[height=2.5cm]{4ptt2.pdf} \hfill
  \includegraphics[height=2.8cm]{4ptt2_1.pdf}
\end{figure}

\vspace{-2em}
\hyperlink{helicity}{
\begin{flushleft}
$
\begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
& \quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*  + \text{remaining 10 terms}\big\}
\end{aligned}
$
\end{flushleft}
}
\end{frame}

@@

    \textbf{传统费曼图计算：}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{5pt.png}
    \end{figure}
\vspace{-1.5em}
\pause
\begin{center}
\hspace*{-0.5em}\includegraphics[width=1.05\textwidth]{structure.png}
\end{center}
\vspace{-1.5em}
\pause
\hspace*{-0.5em}\textcolor{red}{We need to cancel many useless information because of gauge redundancies!}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
\pause
$M_5=\!\!\!\!\!\!\underbrace{A_5[12345]}_{\textcolor{red}{\text{Color-ordered Amplitudes}}}\mathrm{Tr}[T^{a_1}T^{a_2}\cdots T^{a_5}]+\text{perms}$ ,\quad$+,-$ : helicity

@@

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-3em}
    \pause
    \begin{gather*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}_\alpha[\lambda|_{\dot{\alpha}},\quad \sigma^\mu=(1,\vec{\sigma}),\\
        \aket{\lambda},\sket{\lambda}: \text{Weyl Spinors}
    \end{gather*}
\end{frame}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
    % 右侧：PT表达式
    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-2em}
    \begin{gather*}
        {A_5[1^-,2^-,3^-,4^-,5^-]=0}\\
        {A_5[1^+,2^-,3^-,4^-,5^-]=0}\\
        \textcolor{red}{A_5[1^+,2^+,3^-,4^-,5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

@@

\begin{frame}
    More specifically,

@@

\pause
\begin{equation*}
    \boxed{\Rightarrow:\quad A[1^+\cdots ~i^-,(i+1)^+\cdots~j^-\cdots n^+]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
\end{equation*}

@@

\begin{columns}[T]
  % 左列：当前已完成
  \begin{column}{0.48\textwidth}
    \begin{block}{\centering\large \textbf{So far: Foundations}}
      \begin{itemize}[left=1em]
        \item Reviewed the structure of \textbf{BCFW recursion relation}
        \item Applied to:
          \begin{itemize}[left=0.1em]
            \item \textbf{Pure Yang-Mills} theory
            \item Tree-level MHV amplitudes
            \item Color-ordered partial amplitudes
          \end{itemize}
      \end{itemize}
    \end{block}
  \end{column}
\pause
  % 右列：研究目标
  \begin{column}{0.48\textwidth}
    \begin{block}{\centering\large \textbf{Next: Realistic Models}}
      \begin{itemize}[left=1em]
        \item Move beyond massless gauge theory
        \item Consider:
          \begin{itemize}[left=0.1em]
            \item \textbf{(De)constructed gauge theories}
          \end{itemize}
        \item Key questions:
          \begin{itemize}[left=0.1em]
            \item Can BCFW still apply?
            \item How to choose momentum shift?
            \item What new structures emerge?
          \end{itemize}
      \end{itemize}
    \end{block}
  \end{column}
\end{columns}

@@

\begin{frame}{Introduction of quiver gauge theory}
\vspace{1em}
\begin{columns}[c]
    \column{0.43\textwidth}
    \centering
    \includegraphics[width=100pt]{Moose.png}

@@

\begin{frame}
    \frametitle{Amplitudes from BCFW}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{2-site.png}
    \end{figure}
    \vspace{-1em}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1^\Phi,2^{\Phi^\dagger},3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi,2^{\Phi^\dagger},3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point colorordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{SQCD like sector}
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$\\
        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
        \begin{gather*}
        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
        \end{gather*}
        The amplitudes can be computed 
        \begin{align*}
            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item $\Phi^\dagger (nV_1)\Phi$
            \begin{equation*}
                A[1,2,\cdots,(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
            \end{equation*}
            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
                A[1,2,3^+,4^+]=0\quad \Rightarrow  \quad A[1,2,3^+,\cdots,n^+]=0 \end{equation*}}
        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
        \end{equation*}       
    \end{itemize}
\end{frame}

@@

    \end{itemize}
    \pause
    For example, if we want to compute $A[1,2,5_1^+,3_1^+,4_1^-,7_2^+,6_2^+,8_2^+]$:
    \begin{equation*}
        A=\frac{\avg{2\textcolor{green}{4}}^2\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{25}{53}\mdavg{34}{41}}\textcolor{red}{\mdavg{27}{76}\mdavg{68}{81}}}
    \end{equation*}
\end{frame}
\section{Summary}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
    \end{itemize}
\end{frame}
\begin{frame} 
    \centering
    \Huge Thanks for your attention!
\end{frame} 
\appendix
\begin{frame}{Spinor-Helicity Formalism}
    \hypertarget{helicity}{}
\begin{block}{Helicity}
\textbf{\hyperlink{conv}{Helicity}} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
\[
h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
\]
\end{block}
\pause
% 文本说明（点击1出现）
\only<1->{
S-matrix is a function of momentum $p_i$ and helicity $h_i$
}

>>>>

\begin{document}
\setbeamertemplate{itemize item}{\normalsize\textbullet}
\begin{frame} % ← 不使用 [plain]，保留 Madrid 顶部蓝条
  \titlepage
\end{frame}
\section{Motivation}
\begin{frame}{Why We Study Scattering Amplitudes?}
  \begin{enumerate}
    \item \textbf{Bridge between theory and experiment}
    \begin{itemize}
      \item Core prediction targets for high-energy collider experiments such as the LHC , especially for high multiplicity amplitudes.
      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
    \end{itemize}
    \pause
    \item \textbf{Reveal deep structures of quantum field theory}
    \begin{itemize}
      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or AdS/CFT correspondence
    \end{itemize}
  \end{enumerate}
\end{frame}

@@

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\pause
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
$n$ pt. amplitudes & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
\# of diagrams      & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
\hline
\end{tabular}
\end{center}
\centering
\textcolor{red}{The number of Feyman diagrams grow quite rapidly!}

@@

\begin{frame}
\frametitle{Conventional Computation}

    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
\begin{figure}
  \centering
  \includegraphics[height=2.5cm]{4ptt2.pdf} \hfill
  \includegraphics[height=2.8cm]{4ptt2_1.pdf}
\end{figure}

\vspace{-2em}

\begin{flushleft}
$
\begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
& \quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*  + \text{remaining 10 terms}\big\}
\end{aligned}
$
\end{flushleft}

@@

    \textbf{传统费曼图计算：}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{5pt.png}
    \end{figure}
\vspace{-1.5em}
\pause
\begin{center}
\hspace*{-0.5em}\includegraphics[width=1.05\textwidth]{structure.png}
\end{center}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Helicity Amplitude}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
\pause
$M_5=\!\!\!\!\!\!\underbrace{A_5[12345]}_{\textcolor{red}{\text{Color-ordered Amplitudes}}}\mathrm{Tr}[T^{a_1}T^{a_2}\cdots T^{a_5}]+\text{permutations}$

@@

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{align*}
    A_5[1^+2^+3^+4^+5^+] &= 0 
    \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
    A_5[1^-2^+3^+4^+5^+] &= 0 
    \qquad 1,2,\cdots,n:~\text{particle labels}) \\
    \end{align*}
    \pause
    \vspace{-3em}
    \hypertarget{conv}{}
    \begin{gather*}
    \textcolor{red}{A_5[1^-2^-3^+4^+5^+]= 
    \frac{\langle 1 2 \rangle^4}
         {\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle45 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trivial one})\\[1em]
    (p_{i\mu} \sigma^\mu)_{\alpha\dot{\alpha}}=(\aket{p_i})_\alpha([p_i|)_{\dot{\alpha}},\quad \aket{p_i}=\aket{i}\\
    \quad \sigma^\mu=(1,\vec{\sigma}),\quad \aket{i},\sket{i}: \text{Weyl Spinors}\\
    \avg{ij}=\langle i |^\alpha \aket{j}_\alpha=\varepsilon^{\alpha\beta}\aket{i}_\beta\aket{j}_\alpha,\quad \varepsilon^{\alpha\beta}: \text{antisymmetric tensor}
    \end{gather*}
\end{frame}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
    % 右侧：PT表达式
    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+2^+3^+4^+5^+]=0}\\
        {A_5[1^-2^+3^+4^+5^+]=0}\\
        \textcolor{red}{A_5[1^-2^-3^+4^+5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-3em}
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

@@

\begin{frame}
    More specifically, it helps us to prove P. T. formula

@@

\vspace{-2em}
\pause
\begin{equation*}
    \boxed{\Rightarrow:\quad A[1^+\cdots ~i^-(i+1)^+\cdots~j^-(j+1)^+\cdots n^+]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
\end{equation*}

@@

\begin{columns}[T]
  % 左列：当前已完成
  \begin{column}{0.48\textwidth}
    \begin{block}{\centering\large \textbf{So far: Foundations}}
      \begin{itemize}[left=1em]
        \item Reviewed the structure of \textbf{BCFW recursion relation}
        \item Applied to:
          \begin{itemize}[left=0.1em]
            \item \textbf{Pure Yang-Mills} theory
            \item Tree-level MHV amplitudes
            \item Color-ordered partial amplitudes
          \end{itemize}
      \end{itemize}
    \end{block}
  \end{column}
\pause
  % 右列：研究目标
  \begin{column}{0.48\textwidth}
    \begin{block}{\centering\large \textbf{Next: Realistic Models}}
      \begin{itemize}[left=1em]
        \item Move beyond massless gauge theory
        \item Consider:
          \begin{itemize}[left=0.1em]
            \item \textbf{(De)constructed gauge theories}
          \end{itemize}
        \item Key questions:
          \begin{itemize}[left=0.1em]
            \item Can BCFW still apply?
            \item What new structures emerge?
          \end{itemize}
      \end{itemize}
    \end{block}
  \end{column}
\end{columns}

@@

\begin{frame}{Introduction of (De)Constructed gauge theory}
\vspace{1em}
\begin{columns}[c]
    \column{0.43\textwidth}
    \centering
    \includegraphics[width=100pt]{Moose.png}

@@

\begin{frame}
    \frametitle{Amplitudes from BCFW}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{2-site.png}
    \end{figure}
    \vspace{-1em}
    From the Lagrangian, we have known that there are only two kinds of 3 point amplitude ($+,-:$ helicity\qquad $\Phi,\Phi^\dagger: \text{charge of scalar}$)
    \begin{gather*}
        A[1^\Phi2^{\Phi^\dagger}3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi2^{\Phi^\dagger}3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+4^+5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-4^-5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point colorordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots i^-\cdots j^-\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{SQCD like sector}
    The amplitudes can be computed like 
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$
        \begin{align*}
            A[1^\Phi2^{\Phi^\dagger}3^+4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1^\Phi2^{\Phi^\dagger}3^+4^+5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item $\Phi^\dagger (nV_1)\Phi$
            \begin{equation*}
                A[1^\Phi2^{\Phi^\dagger}\cdots(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
            \end{equation*}
            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
                A[1^\Phi2^{\Phi^\dagger}3^+4^+]=0\quad \Rightarrow  \quad A[1^\Phi2^{\Phi^\dagger}3^+\cdots n^+]=0 \end{equation*}}
        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^+6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
        \end{equation*}       
    \end{itemize}
\end{frame}

@@

    \end{itemize}
    \pause
    For example, if we want to compute $A[1^\Phi2^{\Phi^\dagger}5_1^+3_1^+4_1^-7_2^+6_2^+8_2^+]$:
    \begin{equation*}
        A=\frac{\avg{2\textcolor{green}{4}}^2\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{25}{53}\mdavg{34}{41}}\textcolor{red}{\mdavg{27}{76}\mdavg{68}{81}}}
    \end{equation*}
    If you use Feynman diagrams, it may take sevral days to accomplish the computation.
\end{frame}
\section{Summary}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
    \end{itemize}
\end{frame}
\begin{frame} 
    \centering
    \Huge Thanks for your attention!
\end{frame} 
\appendix
\begin{frame}{Spinor-Helicity Formalism}
    \hypertarget{helicity}{}
\begin{block}{Helicity}
\textbf{\hyperlink{conv}{Helicity}} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
\[
h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
\]
\end{block}
\pause
% 文本说明（点击1出现）
\only<1->{
S-matrix is a function of momentum $p_i$ and helicity $h_i$
}
